DataCamp: An Interactive Teaching Tool

### 2018-01-19 manuscript.tex
final edits

\subsubsection{Gamification}
Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
progress (points and chapters completed) as well as the progress of their peers. Students will often perform better
in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution.

@@

\subsection{Pre-existing R courses}
In order to utilize 
DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, access is facilitated 
by adding students to the DataCamp group by supplying university email addresses on the \textit{Members} tab, or by creating an integration to your LMS.
\section{Creating a DataCamp Course}
\subsection{Getting Started}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
a GitHub account (\url{https://github.com}). (Should this be in section 3.5.2? -- Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code.) The simplest way to begin building the course is to use the template course files from the
\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
made through DataCamp will update the GitHub repository and vice versa.

@@

\subsection{Course Editing}
Educators are able to edit their courses in a number of ways, but the \texttt{Teach Editor} located in the DataCamp dashboard is the
most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
viewing.
\subsection{Components of a DataCamp Course}
\subsubsection{Exercise Layout}
Figure1 is an example of an exercise in the Teach Editor and figure2 is the corresponding interface for students. Students will read the lesson information and instructions, answer the question, and submit their code; it is recommended that each exercise takes approximately 5 minutes.
\begin{figure}
\caption{Teach Editor Interface}
\begin{Verbatim}[frame=single]
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

\begin{verbatim}
Multiple choice exercises use the SCT function called  \texttt{test_mc} 
which requires two arguments: \texttt{correct} and \texttt{feedback_msgs}. 
The \texttt{correct} argument specifies the position of the correct answer;
if the correct answer is the second option listed, then set \texttt{correct = 2}. 
The \texttt{feedback_msgs} argument is a vector of strings that contain feedback 
messages corresponding to the positions of the listed options.

\end{verbatim}
\subsection{Advise for smoother course development}
DataCamp is fairly new and the only available information about course creation is on the DataCamp website. While the documentation on DataCamp is comprehensive, here are some tips for developing a first course.

@@

\subsubsection{Collaboration for course development}
To add collaborators to the course, go to the course repository
on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
to uncheck `My Courses' in order to view and contribute to the repository.
\subsubsection{Integrating R packages}
Information on how to add data sets and images to a course
can be found in DataCamps \textit{Teach} documentation \url{https://www.datacamp.com/teach/documentation} under the `Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named \texttt{requirements.r}. This file should contain a line of code with three components: \texttt{devtools::install\_version}, package name and version for 
every package you wish to include in the DataCamp course. For example, the following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.

>>>>

\subsubsection{Gamification}
Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
progress (points and chapters completed) as well as the progress of their peers. When students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution.

@@

\subsection{Pre-existing R courses}
In order to utilize 
DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, access is facilitated 
by adding students to the DataCamp group by supplying university email addresses on the \textit{Members} tab, or by creating an integration to your LMS.
\section{Creating a DataCamp Course}
\subsection{Getting Started}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
a GitHub account (\url{https://github.com}). The simplest way to begin building the course is to use the template course files from the
\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
made through DataCamp will update the GitHub repository and vice versa.

@@

\subsection{Course Editing}
Educators are able to edit their courses in a number of ways, but the \texttt{Teach Editor} located in the DataCamp dashboard is the
most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
viewing.
\subsection{Components of a DataCamp Course}
\subsubsection{Exercise Layout}
Figure1 is an example of an exercise in the Teach Editor and figure2 is the corresponding interface for students. Students will read the lesson information and instructions, answer the question, and submit their code.
\begin{figure}
\caption{Teach Editor Interface}
\begin{Verbatim}[frame=single]
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

Multiple choice exercises use the SCT function called  \texttt{test\_mc} 
which requires two arguments: \texttt{correct} and \texttt{feedback\_msgs}. 
The \texttt{correct} argument specifies the position of the correct answer;
if the correct answer is the second option listed, then set \texttt{correct = 2}. 
The \texttt{feedback\_msgs} argument is a vector of strings that contain feedback 
messages corresponding to the positions of the listed options.

\subsection{Advise for smoother course development}
DataCamp is fairly new and the only available information about course creation is on the DataCamp website. While the documentation on DataCamp is comprehensive, here are some tips for developing a first course.

@@

\subsubsection{Collaboration for course development}
Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. 
To add collaborators to the course, go to the course repository
on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
to uncheck `My Courses' in order to view and contribute to the repository.
\subsubsection{Integrating R packages}
Information on how to add data sets and images to a course
can be found in DataCamps \textit{Teach} documentation \url{https://www.datacamp.com/teach/documentation} under the `Upload Assets' tab. However,
there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
in the GitHub course repository named \texttt{requirements.r}. This file should contain a line of code with three components: \texttt{devtools::install\_version}, package name and version for 
every package you wish to include in the DataCamp course. For example, the following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
